---
title: "Data preprocessing"
date: "`r Sys.Date()`"
output: 
  rmdformats::downcute:
    self_contained: true
    highlight: kate
    toc_depth: 3
    default_style: dark
    code_folding: hide
    code_download: true
    highlight_downlit: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(
  cache = TRUE,
  warnings = FALSE,
  messages = FALSE
)

library(tidyverse)
library(sf)
```


# Import data

```{r}
serology <- read_csv("./01_data/raw/FFI.peru.serology.kmeans2.4000.csv") %>%
  rename(ffi_is_code = Codigo) %>%
  select(-1)

ffi_individual <- read_csv("./01_data/raw/individuals_result_share_072022.csv")
ffi_household <- read_csv("./01_data/raw/household_gps_share_072022.csv")
ffi_2000_2019 <- read_csv("./01_data/raw/Data_FFI_2000_2019_20212405.csv")
ffi_2020_2021 <- read_csv("./01_data/raw/Data_FFI_2020_2021_20210629.csv")
poblacion <- readRDS("./01_data/raw/poblacion_inei_2017.rds")
```

# Format data

## FFI 2000-2021

```{r}
data_malaria <- bind_rows(ffi_2000_2019, 
                          ffi_2020_2021) 

data_malaria_long <- data_malaria %>%
  filter(District %in% c("BELEN", "INDIANA")) %>% 
  select(
    "District", 
    "Health Facility Name", 
    "Date by month",
    "Year", "Month", 
    "Confirmed P. Falciparum",
    "Confirmed P. Vivax"
  ) %>%
  pivot_longer(
    cols = 6:7, 
    names_to = "malaria",
    values_to = "cases"
  )
```

## Individuals

```{r}
ffi_total <- ffi_individual %>%
  full_join(
    serology %>%
      mutate(
        ffi_is_code = paste0(0, ffi_is_code)
      ),
    by = "ffi_is_code"
  )

ffi_is_symp_top3 <- ffi_total %>%
  pivot_longer(
    cols = ffi_is_symp_month_head:ffi_is_symp_month_nosymptopm,
    names_to = "ffi_is_symp",
    values_to = "ffi_is_symp_ans"
  ) %>% 
  count(ffi_is_symp, ffi_is_symp_ans) %>% 
  filter(ffi_is_symp_ans != 0,
         ffi_is_symp != "ffi_is_symp_month_nosymptopm") %>%
  slice_max(n, n = 3)

ffi_total <- ffi_total %>%
  mutate(
    ffi_is_district = fct_recode(
      ffi_is_district,
      "Indiana" = "INDIANA",
      "Belen" = "BELEN"
    ),
    age_cat = case_when(
      ffi_is_age_fixed >= 70 ~ "[70+)",
      ffi_is_age_fixed >= 60 ~ "[60-70)",
      ffi_is_age_fixed >= 50 ~ "[50-60)",
      ffi_is_age_fixed >= 40 ~ "[40-50)",
      ffi_is_age_fixed >= 30 ~ "[30-40)",
      ffi_is_age_fixed >= 20 ~ "[20-30)",
      ffi_is_age_fixed >= 10 ~ "[10-20)",
      ffi_is_age_fixed >= 0 ~ "[0-10)"
    ),
    age_cat = factor(age_cat),
    age_code = case_when(
      age_cat == "[70+)" ~ 8,
      age_cat == "[60-70)" ~ 7,
      age_cat == "[50-60)" ~ 6,
      age_cat == "[40-50)" ~ 5,
      age_cat == "[30-40)" ~ 4,
      age_cat == "[20-30)" ~ 3,
      age_cat == "[10-20)" ~ 2,
      age_cat == "[0-10)" ~ 1,
    ),
    gender = factor(
      ffi_is_sex,
      labels = c("Male", "Female")
    ),
    ffi_is_malaria = factor(
      ffi_is_malaria,
      labels = c("No", "Yes", "Don't Know / No Answer")
    ),
    across(
      c(pf_recent:pv_historic),
      ~ factor(., labels = c("Negative", "Positive"))
    ),
    across(
      c(
        ffi_is_fever_month,
        ffi_is_antimal_drug_use, 
        ffi_is_mosq_net
      ),
      ~ factor(., labels = c("No", "Yes"))
    ),
    ffi_is_trip_month = factor(
      ffi_is_trip_month,
      labels = c("No", "Yes", "Don't Know/No Answer")
    ),
    ffi_is_mal_lifetime = factor(
      ffi_is_mal_lifetime,
      labels = c(
        "1 to 3 times",
        "3 to 7 times",
        "More than 7 times"
      )
    ),
    ffi_is_place_shower = factor(
      ffi_is_place_shower,
      labels = c(
        "Bathroom inside the dwelling",
        "Bathroom outside the dwelling",
        "In the countryside/river",
        "Other"
      )
    ),
    education_level = case_when(
      ffi_is_inst_level %in% 0 ~ "No schooling", 
      ffi_is_inst_level %in% 1:2 ~ "Primary school",
      ffi_is_inst_level %in% 3:4 ~ "Secondary school",
      ffi_is_inst_level %in% 5:6 ~ "Higher education"
    ),
    education_level = fct_relevel(education_level, "No schooling",
                                  "Primary school",
                                  "Secondary school"),
    economic_activities = factor(ffi_is_main_econ_act,
                                 labels = c("None",
                                            "Day labourer",
                                            "Wood extractor",
                                            "Fisherman",
                                            "Livestock farmer",
                                            "Farmer",
                                            "Trader",
                                            "Housewife",
                                            "Student",
                                            "Motorcycle taxi driver",
                                            "Other")),
    economic_activities2 = fct_collapse(
      economic_activities,
      "Forest Related" = c("Day labourer",
                           "Wood extractor",
                           "Fisherman",
                           "Livestock farmer",
                           "Farmer"),
      "Housewife/student" = c("Housewife",
                              "Student"),
      "Others" = c("Motorcycle taxi driver",
                   "Other")
    ),
    ffi_is_place_sleep = factor(ffi_is_place_sleep,
                                labels = c("Inside the dwelling",
                                           "Outside the dwelling",
                                           "Don't Know / Don't Answer")),
    ffi_is_mosq_net_freq = factor(ffi_is_mosq_net_freq,
                                  levels = c(0:2, 99),
                                  labels = c("Never",
                                             "Every day",
                                             "Sometimes",
                                             "Don't Know / Don't Answer")),
    across(
      c(ffi_is_symp_month_head,
        ffi_is_symp_month_musclejoint,
        ffi_is_symp_month_general),
      ~ factor(
        .,
        labels = c("No", "Yes")
      )
    ),
    ffi_is_knowl_mal_inf = factor(ffi_is_knowl_mal_inf,
                                  labels = c("I was diagnosed at the health facility",
                                             "Because of symptoms",
                                             "Other")),
    pv_exposure = case_when(
      pv_recent == "Negative" & pv_historic == "Negative" ~ "Negative",
      is.na(pv_recent) & is.na(pv_historic) ~ NA_character_,
      TRUE ~ "Positive"
    ),
    pf_exposure = case_when(
      pf_recent == "Negative" & pf_historic == "Negative" ~ "Negative",
      is.na(pf_recent) & is.na(pf_historic) ~ NA_character_,
      TRUE ~ "Positive"
    ),
    recent_exposure = case_when(
      pv_recent == "Negative" & pf_recent == "Negative" ~ "Negative",
      is.na(pv_recent) & is.na(pf_recent) ~ NA_character_,
      TRUE ~ "Positive"
    ),
    historical_exposure = case_when(
      pv_historic == "Negative" & pf_historic == "Negative" ~ "Negative",
      is.na(pv_historic) & is.na(pf_historic) ~ NA_character_,
      TRUE ~ "Positive"
    ),
    any_pv_pf_exposure = case_when(
      recent_exposure == "Negative" & historical_exposure == "Negative" ~ "Negative",
      is.na(recent_exposure) & is.na(historical_exposure) ~ NA_character_,
      TRUE ~ "Positive"
    ),
    only_pv_exposure = case_when(
      pv_exposure == "Positive" & pf_exposure == "Negative" ~ "Positive", 
      is.na(pv_exposure) & is.na(pf_exposure) ~ NA_character_,
      TRUE ~ "Negative"
    ),
    only_pf_exposure = case_when(
      pf_exposure == "Positive" & pv_exposure == "Negative" ~ "Positive", 
      is.na(pf_exposure) & is.na(pv_exposure) ~ NA_character_,
      TRUE ~ "Negative"
    ),
    pv_pf_exposure = case_when(
      pv_exposure == "Positive" & pf_exposure == "Positive" ~ "Positive",
      is.na(pv_exposure) & is.na(pf_exposure) ~ NA_character_,
      TRUE ~ "Negative"
    ),
    freedom_malaria = case_when(
      pv_exposure == "Negative" & pf_exposure == "Negative" ~ "Positive", 
      is.na(pv_exposure) & is.na(pf_exposure) ~ NA_character_,
      TRUE ~ "Negative"
    ),
    only_pv_recent = case_when(
      pv_recent == "Positive" & pf_recent == "Negative" ~ "Positive", 
      is.na(pv_recent) & is.na(pf_recent) ~ NA_character_,
      TRUE ~ "Negative"
    ),
    only_pf_recent = case_when(
      pf_recent == "Positive" & pv_recent == "Negative" ~ "Positive", 
      is.na(pf_recent) & is.na(pv_recent) ~ NA_character_,
      TRUE ~ "Negative"
    ),
    pv_pf_recent = case_when(
      pv_recent == "Positive" & pf_recent == "Positive" ~ "Positive",
      is.na(pv_recent) & is.na(pf_recent) ~ NA_character_,
      TRUE ~ "Negative"
    ),
    freedom_malaria_recent = case_when(
      pv_recent == "Negative" & pf_recent == "Negative" ~ "Positive", 
      is.na(pv_recent) & is.na(pf_recent) ~ NA_character_,
      TRUE ~ "Negative"
    ),
    only_pv_historic = case_when(
      pv_historic == "Positive" & pf_historic == "Negative" ~ "Positive", 
      is.na(pv_historic) & is.na(pf_historic) ~ NA_character_,
      TRUE ~ "Negative"
    ),
    only_pf_historic = case_when(
      pf_historic == "Positive" & pv_historic == "Negative" ~ "Positive", 
      is.na(pf_historic) & is.na(pv_historic) ~ NA_character_,
      TRUE ~ "Negative"
    ),
    pv_pf_historic = case_when(
      pv_historic == "Positive" & pf_historic == "Positive" ~ "Positive",
      is.na(pv_historic) & is.na(pf_historic) ~ NA_character_,
      TRUE ~ "Negative"
    ),
    freedom_malaria_historic = case_when(
      pv_historic == "Negative" & pf_historic == "Negative" ~ "Positive", 
      is.na(pv_historic) & is.na(pf_historic) ~ NA_character_,
      TRUE ~ "Negative"
    ),
    across(c(pv_exposure:freedom_malaria_historic), factor)
  )


labelled::var_label(ffi_total) <- list(
  ffi_is_district = "Districs",
  gender = "Gender",
  ffi_is_age = "Age",
  education_level = "Education Level",
  economic_activities = "Economic Activities",
  economic_activities2 = "Economic Activities",
  ffi_is_trip_month = "Trip in the last month",
  ffi_is_place_shower	= "Usual places to bathe",
  ffi_is_place_sleep = "Place to sleep last night",
  ffi_is_mosq_net = "Mosquito Net",
  ffi_is_mosq_net_freq = "Frequency of Mosquito Net",
  ffi_is_malaria = "Ever had malaria",
  ffi_is_fever_month = "History of fever in the last month",
  ffi_is_knowl_mal_inf = "Knowledge of whether it was malaria",
  ffi_is_symp_month_head = "Symptoms or signs in the last month: Headache",
  ffi_is_symp_month_musclejoint = "Symptoms or signs in the last month: Muscle or joint pain",
  ffi_is_symp_month_general = "Symptoms or signs in the last month: General malaise",
  pf_recent = "Recent P. Falciparum",
  pf_historic = "Historical P. Falciparum",
  pv_recent = "Recent P. Vivax",
  pv_historic = "Historical P. Vivax",
  pv_exposure = "P. Vivax Exposure",
  pf_exposure = "P. Falciparum Exposure"
)
```

## Household

```{r}
ffi_household <- ffi_household %>% 
  mutate(
    ffi_h_district = fct_recode(
      ffi_h_district,
      "Indiana" = "INDIANA",
      "Belen" = "BELEN"
    ),
    ffi_h_type = factor(ffi_h_type,
                        labels = c("HOUSE TYPE A: House without walls, with or without wooden floor",
                                   "HOUSE TYPE B: House that has one, two or three walls without completely enclosing a room, with or without wooden floor",
                                   "HOUSE TYPE C: House that has at least one room enclosed, with or without wooden floor",
                                   "HOUSE TYPE D: Completely enclosed house, with or without wooden floor")),
    ffi_h_sprayed = factor(ffi_h_sprayed,
                           labels = c("No", "Yes",
                                      "Don't know / No answer")),
    ffi_h_watersource = factor(ffi_h_watersource,
                               levels = c(1:6, 88, 99),
                               labels = c("Drinking water inside the house",
                                          "Drinking water outside the house",
                                          "Well",
                                          "Public well",
                                          "River or stream",
                                          "Rainwater",
                                          "Other",
                                          "Don't know/No answer"))
  )

labelled::var_label(ffi_household) <- list(
  ffi_h_district = "District",
  ffi_h_mti = "Insecticide-treated mosquito nets",
  ffi_h_type = "Type of house",
  ffi_h_sprayed = "Househould sprayed with insecticides in the last 12 months by the ministry of health",
  ffi_h_watersource = "Main source of water for human consumption (food preparation)"
)
```


# Distance Group about communities (Method Sampling)

```{r}
communities_sf <- ffi_household %>%
  select(
    ffi_h_district,
    ffi_h_health_facility_name,
    ffi_h_code_community,
    ffi_h_community,
    ffi_gps_long,
    ffi_gps_lat
  ) %>%
  st_as_sf(
    coords = c("ffi_gps_long", "ffi_gps_lat"),
    crs = 4326
  ) %>%
  group_by(ffi_h_district, ffi_h_health_facility_name, ffi_h_code_community, ffi_h_community) %>%
  summarise() %>%
  st_centroid()

names_hf <- ffi_household %>% 
  count(ffi_h_health_facility_name) %>% 
  pull(ffi_h_health_facility_name)

hf_shp <- readRDS("01_data/raw/HF_shp.rds")

hf_shp <- hf_shp %>% 
  filter(`Health Facility Name` %in% names_hf) %>% 
  select(District, 
         ffi_h_health_facility_name = `Health Facility Name`)
```

## Distance communities and their HF's

```{r}
communities_distances_hf_sampling <- communities_sf %>% 
  ungroup() %>% 
  st_transform(crs = 32718) %>% 
  st_distance(
    hf_shp %>% 
      st_transform(crs = 32718)
  ) %>% 
  as_tibble() 

names(communities_distances_hf_sampling) <- hf_shp$ffi_h_health_facility_name

communities_distances_hf_sampling <- communities_distances_hf_sampling %>% 
  mutate(
    ffi_is_community = communities_sf$ffi_h_community,
    ffi_is_district = communities_sf$ffi_h_district,
    .before = 1
  ) %>% 
  pivot_longer(
    cols = -c(ffi_is_community, ffi_is_district),
    names_to = "ffi_is_health_facility_name",
    values_to = "distance_to_hf_sampl_num"
  ) %>% 
  mutate(distance_to_hf_sampl_num = as.numeric(distance_to_hf_sampl_num))

communities_distances_hf_sampling_cat <- communities_sf %>% 
  as_tibble() %>% 
  ungroup() %>% 
  select(
    ffi_is_district = ffi_h_district,
    ffi_is_health_facility_name = ffi_h_health_facility_name, 
    ffi_is_community = ffi_h_community
  ) %>% 
  left_join(
    communities_distances_hf_sampling
  )

communities_distances_hf_sampling_cat <- communities_distances_hf_sampling_cat %>% 
  group_by(ffi_is_health_facility_name) %>% 
  mutate(
    distance_to_hf_sampl = as.numeric(cut_number(distance_to_hf_sampl_num, 4)),
    distance_to_hf_sampl = factor(distance_to_hf_sampl, 
                                  labels = c("Proximate Distance", "Medium Distance",
                                             "Long Distance", "Extreme Distance"))
  ) %>% 
  ungroup()
```

Update info:

```{r}
ffi_total <- ffi_total %>% 
  left_join(
    communities_distances_hf_sampling_cat
  ) 
```



## Distance communities and Regional Hospital

```{r}
iquitos_centro <- tibble(
  "ffi_h_health_facility_name" = "Hospital Regional de Loreto",
  Longitude = -73.25385902080906,
  Latitude = -3.7264060164148716,
) %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326) %>%
  st_transform(crs = 32718)

communities_distances_rh_sampling <- communities_sf %>%
  st_transform(crs = 32718) %>%
  st_distance(iquitos_centro)

communities_distances_rh_sampling <- enframe(communities_distances_rh_sampling) %>%
  mutate(
    ffi_is_cod_com = communities_sf$ffi_h_code_community,
    ffi_is_community = communities_sf$ffi_h_community,
    distance_to_rh_sampl_num = as.numeric(value),
    ffi_is_district = communities_sf$ffi_h_district
  ) %>%
  select(-c(name, value)) %>% 
  group_by(ffi_is_district) %>% 
  mutate(
    distance_to_rh_sampl = as.numeric(cut_number(distance_to_rh_sampl_num, 4)),
    distance_to_rh_sampl = factor(distance_to_rh_sampl, 
                                  labels = c("Proximate Distance", "Medium Distance",
                                             "Long Distance", "Extreme Distance"))
  ) %>% 
  ungroup()
```

Las Comunidades mas cercanas y mas lejanas por distrito:

```{r eval=FALSE}
communities_distances_rh_sampling %>%
  group_by(ffi_is_district) %>%
  slice_min(distance_to_rh_sampl, n = 1) %>%
  bind_rows(
    communities_distances_rh_sampling %>%
      mutate(
        ffi_is_district = communities_sf$ffi_h_district
      ) %>%
      group_by(ffi_is_district) %>%
      slice_max(distance_to_rh_sampl, n = 1)
  ) %>%
  arrange(ffi_is_district, distance_to_rh_sampl)
```

Update info:

```{r}
ffi_total <- ffi_total %>% 
  left_join(
    communities_distances_rh_sampling 
  ) 
```

## Distance communities to Regional Hospital and Health Facilities (min distance)

```{r}
ffi_total <- ffi_total %>% 
  rowwise() %>% 
  mutate(
    distance_to_rh_hf_sampl_num = min(distance_to_rh_sampl_num, distance_to_hf_sampl_num)
  ) %>% 
  group_by(ffi_is_district) %>% 
  mutate(
    distance_to_rh_hf_sampl = as.numeric(cut_number(distance_to_rh_hf_sampl_num, 4)),
    distance_to_rh_hf_sampl = factor(distance_to_rh_hf_sampl,
                                     labels = c("Proximate Distance", "Medium Distance",
                                                "Long Distance", "Extreme Distance"))
  ) %>% 
  ungroup()


labelled::var_label(ffi_total) <- list(
  distance_to_rh_hf_sampl = "Distance Category to Regional Hospital and Health Facilities"
)


ffi_total %>% 
  group_by(ffi_is_district, distance_to_rh_hf_sampl) %>% 
  summarise(
    min = min(distance_to_rh_hf_sampl_num),
    max = max(distance_to_rh_hf_sampl_num),
    mean = mean(distance_to_rh_hf_sampl_num),
    median = median(distance_to_rh_hf_sampl_num)
  )
```

# Distance Group about communities (Method Census)

```{r}
comunidades_info_total <- readRDS("01_data/raw/Información poblacional comunidades.RData") %>%
  st_as_sf()

#https://stackoverflow.com/a/54133105

st_geometry(comunidades_info_total)[
  comunidades_info_total$MNOMCP == "8 DE DICIEMBRE"
] <- st_point(c(-73.248636296,
                -3.777654358))
st_geometry(comunidades_info_total)[
  comunidades_info_total$MNOMCP == "CABO LOPEZ"
] <- st_point(c(-73.253457539,
                -3.781405681))
st_geometry(comunidades_info_total)[
  comunidades_info_total$MNOMCP == "TIMICURO GRANDE"
] <- st_point(c(-73.023866667,
                -3.558536667))

# comunidades_info_total <- comunidades_info_total %>%
#   mutate(
#     geometry2 = case_when(
#       MNOMCP == "8 DE DICIEMBRE" ~ st_cast(
#         st_sfc(st_point(c(-73.248636296,
#                           -3.777654358))),
#         "GEOMETRY"
#         ),
#       MNOMCP == "CABO LOPEZ" ~ st_cast(
#         st_sfc(st_point(c(-73.253457539,
#                           -3.781405681))),
#         "GEOMETRY"
#         ),
#       MNOMCP == "TIMICURO GRANDE" ~ st_cast(
#         st_sfc(st_point(c(-73.023866667,
#                           -3.558536667))),
#         "GEOMETRY"
#         ),
#       TRUE ~ st_cast(geometry, "GEOMETRY")
#       )
#   )


comunidades_info_adic <- comunidades_info_total %>%
  filter(st_is_empty(geometry)) %>%
  st_drop_geometry() %>%
  distinct(MNOMCP, .keep_all = TRUE) %>%
  filter(`Health Facility Name` %in% hf_shp$ffi_h_health_facility_name) %>%
  mutate(District = str_to_title(District)) %>% 
  left_join(
    communities_sf %>%
      select(
        District = ffi_h_district,
        `Health Facility Name` = ffi_h_health_facility_name,
        MNOMCP = ffi_h_community,
        geometry
      ),
    by = join_by(District, `Health Facility Name`, MNOMCP)
  )


comunidades_info_total <- comunidades_info_total %>%
  filter(!st_is_empty(geometry)) %>%
  distinct(MNOMCP, .keep_all = TRUE) %>%
  bind_rows(
    comunidades_info_adic
  )
```

## Distance communities and their HF's

```{r}
communities_distances_hf <- comunidades_info_total %>%
  filter(`Health Facility Name` %in% hf_shp$ffi_h_health_facility_name) %>%
  st_as_sf(crs = 4326) %>%
  st_transform(crs = 32718) %>%
  st_distance(
    hf_shp %>%
      st_transform(crs = 32718)
  ) %>%
  as_tibble()

names_comunities_9_hf <- comunidades_info_total %>%
  filter(`Health Facility Name` %in% hf_shp$ffi_h_health_facility_name) %>%
  pull(MNOMCP)

names_districts_9_hf <- comunidades_info_total %>%
  filter(`Health Facility Name` %in% hf_shp$ffi_h_health_facility_name) %>%
  pull(District)

names(communities_distances_hf) <- hf_shp$ffi_h_health_facility_name

communities_distances_hf <- communities_distances_hf %>%
  mutate(
    ffi_is_community = names_comunities_9_hf,
    ffi_is_district = names_districts_9_hf,
    .before = 1
  ) %>%
  pivot_longer(
    cols = -c(ffi_is_community, ffi_is_district),
    names_to = "ffi_is_health_facility_name",
    values_to = "distance_to_hf_census_num"
  ) %>%
  mutate(distance_to_hf_census_num = as.numeric(distance_to_hf_census_num))

communities_distances_hf_total <- comunidades_info_total %>%
  filter(`Health Facility Name` %in% hf_shp$ffi_h_health_facility_name) %>%
  select(
    ffi_is_district = District,
    ffi_is_health_facility_name = `Health Facility Name`,
    ffi_is_community = MNOMCP
  ) %>%
  left_join(
    communities_distances_hf
  )


communities_distances_hf_cat <- communities_distances_hf_total %>%
  filter(ffi_is_health_facility_name != "SOLEDAD DE VILLA BELEN") %>%
  group_by(ffi_is_health_facility_name) %>%
  mutate(
    distance_to_hf_census = as.numeric(cut_number(distance_to_hf_census_num, 4)),
    distance_to_hf_census = factor(
      distance_to_hf_census,
      labels = c(
        "Proximate Distance",
        "Medium Distance",
        "Long Distance",
        "Extreme Distance"
      )
    )
  ) %>%
  ungroup() %>%
  bind_rows(
    communities_distances_hf_total %>%
      filter(ffi_is_health_facility_name == "SOLEDAD DE VILLA BELEN") %>%
      mutate(
        distance_to_hf_census = factor("Medium Distance", 
                                       levels = c(
                                        "Proximate Distance",
                                        "Medium Distance",
                                        "Long Distance",
                                        "Extreme Distance"
                                      ))
      )
  ) %>% 
  mutate(ffi_is_district = str_to_title(ffi_is_district)) %>% 
  st_drop_geometry()
```

Update info:

```{r}
ffi_total <- ffi_total %>%
  left_join(
    communities_distances_hf_cat
  )
```


## Distance communities and Regional Hospital

```{r}
communities_distances_rh <- comunidades_info_total %>% 
  st_as_sf(crs = 4326) %>% 
  st_transform(crs = 32718) %>% 
  st_distance(
    iquitos_centro
  ) %>% 
  enframe() %>% 
  mutate(
    ffi_is_community = comunidades_info_total$MNOMCP,
    distance_to_rh_census_num = as.numeric(value),
    ffi_is_district = comunidades_info_total$District
  ) %>%
  select(-c(name, value))
```

```{r}
communities_distances_rh_cat <- communities_distances_rh %>%
  drop_na(distance_to_rh_census_num) %>%
  arrange(ffi_is_district, distance_to_rh_census_num) %>%
  mutate(
    distance_to_rh_census = as.numeric(cut_number(distance_to_rh_census_num, 4)),
    distance_to_rh_census = factor(
      distance_to_rh_census,
      labels = c(
        "Proximate Distance",
        "Medium Distance",
        "Long Distance",
        "Extreme Distance"
      )
    )
  ) %>%
  ungroup() %>%
  distinct(ffi_is_community, ffi_is_district, .keep_all = TRUE) %>% 
  mutate(ffi_is_district = str_to_title(ffi_is_district))
```

Update info:

```{r}
# ffi_total <- ffi_total %>% 
#   left_join(
#     communities_distances_rh_cat
#   )
# 
# ffi_total %>% 
#   # slice(82, 783) %>% 
#   select(ffi_is_community, ffi_is_district) %>% 
#   left_join(
#     communities_distances_rh_cat
#   )
```


# Export data

```{r eval = FALSE}
saveRDS(ffi_total, 
        file = "01_data/processed/ffi_total.rds")
saveRDS(ffi_household,
        file = "01_data/processed/ffi_household.rds")
saveRDS(data_malaria, 
        file = "01_data/processed/data_malaria.rds")
saveRDS(data_malaria_long,
        file = "01_data/processed/data_malaria_long.rds")
saveRDS(communities_sf ,
        file = "01_data/processed/communities_sf.rds")
saveRDS(hf_shp,
        file = "01_data/processed/hf_shp.rds")
```

