---
title: "Descriptive analysis"
date: "`r Sys.Date()`"
output: 
  rmdformats::downcute:
    self_contained: true
    highlight: kate
    toc_depth: 3
    default_style: dark
    code_folding: hide
    code_download: true
    highlight_downlit: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(
  cache = TRUE,
  warnings = FALSE,
  messages = FALSE
)

library(tidyverse)
library(sf)
library(ggsflabel)
source("03_functions/seropositivy_summarise.R")
```

# Import data

```{r}
ffi_total <- readRDS(file = "01_data/processed/ffi_total.rds")
ffi_household <- readRDS(file = "01_data/processed/ffi_household.rds")
data_malaria <- readRDS(file = "01_data/processed/data_malaria.rds")
data_malaria_long <- readRDS(file = "01_data/processed/data_malaria_long.rds")
communities_sf <- readRDS(file = "01_data/processed/communities_sf.rds")
hf_shp <- readRDS(file = "01_data/processed/hf_shp.rds")
poblacion <- readRDS("./01_data/raw/poblacion_inei_2017.rds")
```


# Figures

## Figure 2


```{r dpi = 300, fig.align='center'}
fig2_malaria_api_belen_indiana_A <- data_malaria_long %>% 
  filter(!(malaria == "Confirmed P. Vivax" & `Date by month` < lubridate::ymd("2009-01-01"))) %>% 
  mutate(
    `Date by month` = lubridate::ceiling_date(`Date by month`,
                                              unit = "year")
  ) %>% 
  group_by(District, malaria, `Date by month`) %>%
  summarise(cases = sum(cases)) %>% 
  ungroup() %>% 
  mutate(
    cases = case_when(
      District == "BELEN" ~ (cases/69608)*1000,
      District == "INDIANA" ~ (cases/11648)*1000,
    )
  ) %>% 
  ggplot(aes(x = `Date by month`, y = cases,
             color = District)) +
  geom_line(linewidth = 0.8) +
  facet_wrap(vars(malaria)) +
  labs(
    x = NULL,
    y = "API"
  ) +
  innovar::scale_color_innova("npr") +
  # geom_hline(yintercept=40, linetype="dashed", 
  #               color = "black", linewidth = 2) +
  # annotate("text", label = "Very low \ntransmission",
  #          y = 35, x = lubridate::ymd("2019-01-01")) +
  theme_minimal()

fig2_malaria_api_belen_indiana_A
```

```{r eval=FALSE}
ggsave("02_output/plots/Fig 2. Malaria Cases in Indiana and Belen, 2000-2021 - A.png", 
       fig2_malaria_api_belen_indiana_A,
       width = 8,
       height = 4,
       dpi = 300,
       bg = "white")
```



```{r dpi = 300, fig.align='center'}
fig2_malaria_api_belen_indiana_B <- data_malaria_long %>% 
  filter(!(malaria == "Confirmed P. Vivax" & `Date by month` < lubridate::ymd("2009-01-01"))) %>% 
  mutate(
    `Date by month` = lubridate::ceiling_date(`Date by month`,
                                              unit = "year")
  ) %>% 
  group_by(District, malaria, `Date by month`) %>%
  summarise(cases = sum(cases)) %>% 
  ungroup() %>% 
  mutate(
    cases = case_when(
      District == "BELEN" ~ (cases/69608)*1000,
      District == "INDIANA" ~ (cases/11648)*1000,
    )
  ) %>% 
  ggplot(aes(x = `Date by month`, y = cases,
             color = District)) +
  geom_line(linewidth = 0.8) +
  facet_wrap(vars(malaria)) +
  labs(
    x = NULL,
    y = "API"
  ) +
  innovar::scale_color_innova("npr") +
  geom_hline(yintercept=100, linetype="dashed", 
                color = "black", linewidth = 2) +
  annotate("text", label = "Very low \ntransmission",
           y = 80, x = lubridate::ymd("2019-01-01")) +
  theme_minimal()

fig2_malaria_api_belen_indiana_B
```


```{r eval=FALSE}
ggsave("02_output/plots/Fig 2. Malaria Cases in Indiana and Belen, 2000-2021 - B.png", 
       fig2_malaria_api_belen_indiana_B,
       width = 8,
       height = 5,
       dpi = 300,
       bg = "white")
```


## Figure 3


```{r}
sero_timeofmalaria_district_distance_rh_hf_sampling <- seropositivy_summarise(
    ffi_total,
    "timeofmalaria",
    age_cat,
    distance_to_rh_hf_sampl
  ) %>%
  ungroup() %>% 
  mutate(
    distance_to_rh_hf_sampl = fct_relevel(distance_to_rh_hf_sampl, 
                                      "Proximate", "Moderate",
                                      "Distant", "Extra Distant")
  ) %>% 
  ggplot(
    aes(
      x = age_cat,
      y = result_exposure,
      color = exposure,
      group = exposure
    )
  ) +
  geom_point() +
  geom_line() +
  facet_grid(
    vars(distance_to_rh_hf_sampl),
    vars(ffi_is_district)    
  ) +
  scale_y_continuous(
    labels = scales::percent_format(),
    #limits = c(0, 0.50)
  ) +
  labs(
    x = "Age",
    y = "Seropositivity",
    title = str_wrap("Seropositivity according to Time of Exposure to malaria by District and distance category of the communities to Loreto Regional Hospital and Health Facilities on a Sampling Basis", 80)
  ) +
  guides(
    color = guide_legend("Malaria")
  ) +
  innovar::scale_color_innova("npr") +
  theme_bw() +
  theme(
    plot.title = element_text(
      size = 14,
      hjust = 0.5,
      face = "bold"
    ),
    strip.text = element_text(
      size = 12,
      face = "bold"
    ),
    legend.title = element_text(
      size = 12,
      face = "bold"
    )
  )

sero_timeofmalaria_district_distance_rh_hf_sampling
```

```{r eval=FALSE}
ggsave(
  "./02_output/plots/Fig 3. Seropositivity according to time of exposure to malaria by district and distance category.png",
  sero_timeofmalaria_district_distance_rh_hf_sampling,
  dpi = 300,
  bg = "white",
  width = 12,
  height = 8.5
)
```


## Figure 4

```{r}
malaria_seropositivity_type_exposure_belen <- ffi_total %>%
  drop_na(pf_recent:pv_historic) %>%
  pivot_longer(
    cols = pf_recent:pv_historic,
    names_to = "malaria",
    values_to = "result_malaria"
  ) %>%
  filter(ffi_is_district == "Belen") %>%
  mutate(
    malaria = case_when(
      malaria == "pf_recent" ~ "Recent P. Falciparum",
      malaria == "pf_historic" ~ "Historical P. Falciparum",
      malaria == "pv_recent" ~ "Recent P. Vivax",
      malaria == "pv_historic" ~ "Historical P. Vivax"
    ),
    ffi_is_community = str_to_title(ffi_is_community),
    ffi_is_community = fct_reorder(
      ffi_is_community,
      distance_to_rh_sampl_num,
      .desc = TRUE
    )
  ) %>%
  ggplot(aes(
    x = ffi_is_community,
    fill = result_malaria
  )) +
  facet_wrap(vars(malaria)) +
  geom_bar(position = "fill", color = "black") +
  coord_flip(ylim = c(0, 0.25)) +
  scale_y_continuous(
    labels = scales::percent_format()
  ) +
  #ggsci::scale_fill_lancet() +
  innovar::scale_fill_innova("npr") +
  labs(
    title = str_wrap("Serological results by plasmodium type of malaria in the Belen District", 100),
    x = "Communities",
    y = "Percentage"
  ) +
  guides(
    fill = guide_legend("Results")
  ) +  
  theme_minimal() +
  theme(
    strip.text = element_text(
      face = "bold",
      size = 11
    ),
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    axis.text = element_text(
      size = 11
    ),
    legend.title = element_text(
      face = "bold",
      size = 11
    )
  )

malaria_seropositivity_type_exposure_belen
```

```{r eval=FALSE}
ggsave(
  "./02_output/plots/Fig 4. Malaria Seropositivity by type of exposure and plasmodium in Belen.png",
  malaria_seropositivity_type_exposure_belen,
  dpi = 300,
  bg = "white",
  width = 10,
  height = 9
)
```

Alternative color:

```{r}
malaria_seropositivity_type_exposure_belen2 <- 
  malaria_seropositivity_type_exposure_belen +
  innovar::scale_fill_innova("dark_green",
                             reverse = TRUE)
malaria_seropositivity_type_exposure_belen2
```

```{r eval=FALSE}
ggsave(
  "./02_output/plots/Fig 4. Malaria Seropositivity by type of exposure and plasmodium in Belen2.png",
  malaria_seropositivity_type_exposure_belen2,
  dpi = 300,
  bg = "white",
  width = 10,
  height = 9
)
```

## Figure 5

```{r}
malaria_seropositivity_type_exposure_indiana <- ffi_total %>%
  drop_na(pf_recent:pv_historic) %>%
  pivot_longer(
    cols = pf_recent:pv_historic,
    names_to = "malaria",
    values_to = "result_malaria"
  ) %>%
  mutate(
    malaria = case_when(
      malaria == "pf_recent" ~ "Recent P. Falciparum",
      malaria == "pf_historic" ~ "Historical P. Falciparum",
      malaria == "pv_recent" ~ "Recent P. Vivax",
      malaria == "pv_historic" ~ "Historical P. Vivax"
    ),
    ffi_is_community = str_to_title(ffi_is_community),
  ) %>%
  filter(ffi_is_district == "Indiana") %>%
  mutate(
    ffi_is_community = fct_reorder(
      ffi_is_community,
      distance_to_rh_sampl_num,
      .desc = TRUE
    )
  ) %>%
  ggplot(aes(
    x = ffi_is_community,
    fill = result_malaria
  )) +
  facet_wrap(vars(malaria)) +
  geom_bar(position = "fill", color = "black") +
  coord_flip(ylim = c(0, 0.25)) +
  scale_y_continuous(
    labels = scales::percent_format()
  ) +
  #ggsci::scale_fill_lancet() +
  innovar::scale_fill_innova("npr") +
  labs(
    title = str_wrap("Serological results by plasmodium type of malaria in the Indiana District", 100),
    x = "Communities",
    y = "Percentage"
  ) +
  guides(
    fill = guide_legend("Results")
  ) +  
  theme_minimal() +
  theme(
    strip.text = element_text(
      face = "bold",
      size = 11
    ),
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    axis.text = element_text(
      size = 11
    ),
    legend.title = element_text(
      face = "bold",
      size = 11
    )
  )

malaria_seropositivity_type_exposure_indiana
```

```{r eval=FALSE}
ggsave(
  "./02_output/plots/Fig 4. Malaria Seropositivity by type of exposure and plasmodium in Indiana.png",
  malaria_seropositivity_type_exposure_indiana,
  dpi = 300,
  bg = "white",
  width = 10,
  height = 9
)
```

Alternative color:

```{r}
malaria_seropositivity_type_exposure_indiana2 <- 
  malaria_seropositivity_type_exposure_indiana +
  innovar::scale_fill_innova("dark_green",
                             reverse = TRUE)
malaria_seropositivity_type_exposure_indiana2
```

```{r eval=FALSE}
ggsave(
  "./02_output/plots/Fig 4. Malaria Seropositivity by type of exposure and plasmodium in Indiana2.png",
  malaria_seropositivity_type_exposure_indiana2,
  dpi = 300,
  bg = "white",
  width = 10,
  height = 9
)
```

## Figure 6 & 7

### Pre-processing

```{r}
ffi_prevalence_by_household <- ffi_total %>% 
  mutate(
    across(
      c(pf_recent:pv_historic, 
        recent_exposure, historical_exposure),
      ~ case_when(
        . == "Positive" ~ 1,
        TRUE ~ 0
      )
    )
  ) %>% 
  group_by(
    ffi_is_district,
    ffi_is_health_facility_name,
    ffi_is_community, 
    ffi_is_cod_com,
    ffi_is_cod_household
  ) %>% 
  summarise(
    examined = n(),
    across(
      c(pf_recent:pv_historic, 
        recent_exposure, historical_exposure),
      sum
    )
  ) %>% 
  ungroup() %>% 
  mutate(
    across(
      c(pf_recent:pv_historic, 
        recent_exposure, historical_exposure),
      ~ ./examined,
      .names = "prevalence_{.col}"
    )
  ) %>% 
  left_join(
    ffi_household %>% 
      select(ffi_is_community = ffi_h_community,
             ffi_is_cod_household = ffi_h_code_household,
             ffi_gps_long, ffi_gps_lat)
  ) %>% 
  mutate(
    cod_id = paste0(ffi_is_cod_com, ffi_is_cod_household)
  )
```


### Spatial Analysis

```{r}
library(spdep)
```

```{r}
ffi_prevalence_by_household_sf <- ffi_prevalence_by_household %>% 
  st_as_sf(
    coords = c("ffi_gps_long", "ffi_gps_lat"),
    crs = 4326
  ) 
  

ffi_prevalence_kmeans <- ffi_prevalence_by_household_sf %>% 
  group_nest(
    ffi_is_district,
    #ffi_is_community
    #ffi_is_health_facility_name
  ) %>% 
  mutate(
    ffi_coords = map(
      data, 
      ~ coordinates(as(., "Spatial"))
    ),
    neigh_nb = map2(
      data, ffi_coords,
      ~ knn2nb(
          knearneigh(
            .y,
            k = 1,
            longlat = TRUE
          ),
          row.names = .x$cod_id
        )
    ),
    neigh_kd1 = pmap(
      list(ffi_coords,
           neigh_nb,
           data),
      ~ dnearneigh(
        ..1,
        d1 = 0, 
        d2 = max(unlist(nbdists(..2, ..1))), 
        row.names = ..3$cod_id
      )
    ),
    self = map(
      neigh_kd1,
      ~ nb2listw(
        .,
        style = "W", 
        zero.policy = TRUE
      )
    )
  )

```

```{r}

breaks <- c(-Inf, -2.58, -1.96, 
            -1.65, 1.65, 1.96,
            2.58, Inf)
labels <- c("Cold spot: 99% confidence", 
            "Cold spot: 95% confidence", 
            "Cold spot: 90% confidence", 
            "PSU Not significant",
            "Hot spot: 90% confidence",
            "Hot spot: 95% confidence",
            "Hot spot: 99% confidence")

ffi_w.getis <- ffi_prevalence_kmeans %>% 
  mutate(
    data_nosf = map(
      data,
      ~ .x %>% 
        st_set_geometry(NULL) %>% 
        pivot_longer(
          cols = c(prevalence_pf_recent:prevalence_historical_exposure),
          names_to = "type_plasmodium",
          values_to = "prevalence"
        ) %>% 
        group_nest(type_plasmodium,
                   .key = "data_nosf")
    )
  ) %>% 
  unnest(data_nosf) %>% 
  mutate(
    LISA = map2(data_nosf,
               self,
               ~ localG(.x$prevalence, .y)),
    LISA_clust = map(LISA,
                     ~ cut(., include.lowest = TRUE,
                           breaks = breaks, 
                           labels = labels)),
    LISA_label_orig = map(LISA,
                          ~ attributes(.)$cluster),
    LISA = map(LISA, as.numeric)
  ) %>% 
  select(
    ffi_is_district,
    #ffi_is_community,
    #ffi_is_health_facility_name,
    type_plasmodium:LISA_label_orig
  ) %>% 
  unnest(cols = c(data_nosf, LISA, 
                  LISA_clust, LISA_label_orig))

```

```{r}
ffi_w.getis <- ffi_w.getis %>% 
  left_join(
    ffi_household %>% 
      select(
        ffi_is_district = ffi_h_district,
        ffi_is_cod_com = ffi_h_code_community,
        ffi_is_cod_household = ffi_h_code_household,
        ffi_gps_lat, 
        ffi_gps_long
      )
  )

w.getis_sf <- ffi_w.getis %>% 
  st_as_sf(coords = c("ffi_gps_long", 
                      "ffi_gps_lat"),
           crs = 4326,
           remove = FALSE)
```


### Ploting - Figure 6


```{r}
data("Peru", package = "innovar")

crop_coordinates <- Peru %>% 
  filter(dep == "LORETO",
         distr %in% c("INDIANA",
                      "BELEN")) %>% 
  st_bbox()

ffi_shp <- Peru %>% 
  st_crop(crop_coordinates)


plot_getis_recent <- w.getis_sf %>% 
  filter(type_plasmodium %in% c("prevalence_pf_recent", 
                                "prevalence_pv_recent",
                                "prevalence_recent_exposure")) %>% 
  mutate(type_plasmodium = fct_relevel(type_plasmodium,
                                       "prevalence_recent_exposure")) %>% 
  ggplot() +
  geom_sf(data = ffi_shp, fill = "#d9ead8") + 
  geom_sf(aes(col = LISA_clust), 
          size = 1.5,
          alpha = 1) +
  geom_sf(data = ffi_shp, fill = NA) + 
  scale_color_manual(
    values = c("#03595c", "#5dafa6", "#87cdb5",
               "grey50",
               "#efc38f", "#e88245", "#e2634b")
  ) +
  # innovar::scale_color_innova("npr", na.value = "grey50") +
  # colorspace::scale_color_discrete_diverging(palette = "Blue-Red",
  #                                limits = labels) +
  facet_wrap(vars(type_plasmodium),
             labeller = labeller(type_plasmodium = c(prevalence_recent_exposure = "Prevalence Recent Exposure",
                                   prevalence_pf_recent = "Prevalence Recent P. Falciparum",
                                   prevalence_pv_recent = "Prevalence Recent P. Vivax"))) +
  labs(color = "Local Indicator of Spatial Association",
       title = "Spatial Analysis for Recent Exposure") +
  #guides(colour = guide_legend(override.aes = list(size=10))) +
  theme_classic(base_size = 12) +
  theme(
    legend.title = element_text(
      face = "bold"
    ),
    plot.title = element_text(
      face = "bold",
      hjust = 0.5
    ),
    strip.text = element_text(
      face = "bold"
    )
  )
plot_getis_recent
```

```{r eval = FALSE}
ggsave("02_output/plots/Fig 6. Spatial Analysis for Recent Exposure.png",
       plot_getis_recent,
       dpi = 400,
       scale = 0.9,
       device = grDevices::png)
```

### Ploting - Figure 7


```{r}
plot_getis_historical <- w.getis_sf %>% 
  filter(type_plasmodium %in% c("prevalence_pf_historic", 
                                "prevalence_pv_historic",
                                "prevalence_historical_exposure")) %>% 
  ggplot() +
  geom_sf(data = ffi_shp, fill = "#d9ead8") + 
  geom_sf(aes(col = LISA_clust), 
          size = 1.5,
          alpha = 1) +
  geom_sf(data = ffi_shp, fill = NA) + 
  scale_color_manual(
    values = c("#03595c", "#5dafa6", "#87cdb5",
               "grey50",
               "#efc38f", "#e88245", "#e2634b")
  ) +
  # innovar::scale_color_innova("npr", na.value = "grey50") +
  # colorspace::scale_color_discrete_diverging(palette = "Blue-Red",
  #                                limits = labels) +
  facet_wrap(vars(type_plasmodium),
             labeller = labeller(type_plasmodium = c(prevalence_historical_exposure = "Prevalence Historic Exposure",
                                   prevalence_pf_historic = "Prevalence Historic P. Falciparum",
                                   prevalence_pv_historic = "Prevalence Historic P. Vivax"))) +
  labs(color = "Local Indicator of Spatial Association",
       title = "Spatial Analysis for Historic Exposure") +
  #guides(colour = guide_legend(override.aes = list(size=10))) +
  theme_classic(base_size = 12) +
  theme(
    legend.title = element_text(
      face = "bold"
    ),
    plot.title = element_text(
      face = "bold",
      hjust = 0.5
    ),
    strip.text = element_text(
      face = "bold"
    )
  )
plot_getis_historical
```

```{r eval = FALSE}
ggsave("02_output/plots/Fig 7. Spatial Analysis for Historical Exposure.png",
       plot_getis_historical,
       dpi = 400,
       scale = 0.9,
       device = grDevices::png)
```

# Table descriptive

```{r}
library(gtsummary)

fisher.test.simulate.p.values <- function(data, variable, by, ...) {
  result <- list()
  test_results <- stats::fisher.test(data[[variable]], data[[by]], simulate.p.value = TRUE)
  result$p <- test_results$p.value
  result$test <- test_results$method
  result
}
```

## Table for district

### Individuals

```{r}
table_1_ind <- ffi_total %>%
  select(
    ffi_is_district,
    gender,
    ffi_is_age,
    education_level,
    economic_activities2,
    ffi_is_trip_month,
    ffi_is_place_shower,
    ffi_is_place_sleep,
    ffi_is_mosq_net,
    ffi_is_mosq_net_freq,
    ffi_is_fever_month,
    ffi_is_malaria,
    ffi_is_symp_month_head,
    ffi_is_symp_month_musclejoint,
    ffi_is_symp_month_general,
    pf_exposure,
    pv_exposure,
    distance_to_rh_hf_sampl
    # ffi_is_knowl_mal_inf,
    # pf_recent:pv_historic
  ) %>%
  #drop_na(pf_recent:pv_historic) %>% 
  tbl_summary(
    by = "ffi_is_district",
    missing = "no",
    # missing_text = "Missing",
    #type = all_dichotomous() ~ "categorical",
    digits = everything() ~ c(0, 1)
  ) %>%
  add_n() %>%
  add_overall(
    last = TRUE,
    digits = everything() ~ c(0, 1)
  ) %>%
  add_p(
     test = list(all_categorical() ~ "fisher.test.simulate.p.values"),
     pvalue_fun = scales::pvalue
  ) %>% 
  bold_p() %>%
  modify_header(label = "**Variable**") %>%
  bold_labels()
  
table_1_ind
```

```{r eval=FALSE}
table_1_ind %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "./02_output/reports/Table 1. Characteristics of the study population.docx")
```


### Households


```{r}
table_1_household <- ffi_household %>%
  select(
    ffi_h_district,
    ffi_h_mti,
    ffi_h_type,
    ffi_h_sprayed,
    ffi_h_watersource
  ) %>%
  tbl_summary(
    by = "ffi_h_district",
    missing_text = "Missing",
    type = all_dichotomous() ~ "categorical",
    digits = everything() ~ c(0, 1)
  ) %>%
  add_n() %>%
  add_overall(
    last = TRUE,
    digits = everything() ~ c(0, 1)
  ) %>%
  add_p(
     test = list(all_categorical() ~ "fisher.test.simulate.p.values"),
     pvalue_fun = scales::pvalue
  ) %>% 
  bold_p() %>%
  modify_header(label = "**Variable**") %>%
  bold_labels()
  
table_1_household
```


```{r eval=FALSE}
table_1_household %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "./02_output/reports/Characteristics of households.docx")
```

## Table for Plasmodium and Exposure Time

```{r}
table2_ind <- ffi_total %>%
  select(
    ffi_is_district,
    gender,
    ffi_is_age,
    economic_activities2,
    ffi_is_trip_month,
    ffi_is_place_shower,
    ffi_is_mosq_net,
    ffi_is_fever_month,
    ffi_is_symp_month_head,
    ffi_is_symp_month_musclejoint,
    ffi_is_symp_month_general,
    ffi_is_malaria,
    distance_to_rh_hf_sampl,
    pf_recent:pv_historic
  ) %>%
  drop_na(pf_recent:pv_historic) %>%
  pivot_longer(
    cols = pf_recent:pv_historic,
    names_to = "exposure",
    values_to = "result_exposure"
  ) %>%
  mutate(
    exposure = case_when(
      exposure == "pf_recent" ~ "P. Falciparum Recent",
      exposure == "pf_historic" ~ "P. Falciparum Historical",
      exposure == "pv_recent" ~ "P. Vivax Recent",
      exposure == "pv_historic" ~ "P. Vivax Historical"
      ),
    exposure = factor(exposure,
                      levels = c("P. Falciparum Recent",
                                 "P. Falciparum Historical",
                                 "P. Vivax Recent",
                                 "P. Vivax Historical"))
  ) %>%
  tbl_strata(
  strata = exposure,
  .tbl_fun =
    ~ .x %>%
        tbl_summary(
          by = result_exposure,
          missing = "no",
          #missing_text = "Missing",
          #type = all_dichotomous() ~ "categorical",
          digits = everything() ~ c(0, 1)
        ) %>%
        add_p(
          test = list(all_categorical() ~ "fisher.test.simulate.p.values"),
          pvalue_fun = scales::pvalue
        ) %>%
        bold_p() %>%
        modify_header(label = "**Variable**") %>%
        bold_labels() 
  ) 

table2_ind_overall <- ffi_total %>%
  select(
    ffi_is_district,
    gender,
    ffi_is_age,
    economic_activities2,
    ffi_is_trip_month,
    ffi_is_place_shower,
    ffi_is_mosq_net,
    ffi_is_fever_month,
    ffi_is_symp_month_head,
    ffi_is_symp_month_musclejoint,
    ffi_is_symp_month_general,
    ffi_is_malaria,
    distance_to_rh_hf_sampl
  ) %>%
  tbl_summary(
    missing = "no",
    # missing_text = "Missing",
    # type = all_dichotomous() ~ "categorical",
    digits = everything() ~ c(0, 1)
  ) %>%
  modify_header(
    label = "**Variable**"
  ) %>%
  bold_labels() %>%
  modify_spanning_header(stat_0 ~ "**Overall**")

table2_ind <- tbl_merge(
  tbls = list(table2_ind, table2_ind_overall),
  tab_spanner = FALSE
)

table2_ind
```

```{r eval=FALSE}
table2_ind %>%
  as_flex_table() %>%
  flextable::save_as_docx(path = "./02_output/reports/Characteristics of study population by P.vivax and falciparum exposure.docx")
```


# Supplementary Figure 1


## Malaria Annual Parasite Index


```{r}
data_malaria <- data_malaria %>%
  drop_na(District)

pob_loreto <- poblacion %>%
  filter(dep == "LORETO") %>%
  select(District = distr, Total)
```


```{r}
malaria_cases_pob <- data_malaria %>%
  rowwise() %>%
  mutate(
    cases_malaria = sum(
      c_across(c(
        `Confirmed P. Falciparum`,
        `Confirmed P. Vivax`
      )),
      na.rm = TRUE
    )
  ) %>%
  group_by(District) %>%
  summarise(cases_malaria = sum(cases_malaria))

malaria_cases_pob <- malaria_cases_pob %>%
  left_join(
    pob_loreto
  ) %>%
  mutate(
    api = cases_malaria * 1000 / Total
  )

data(Peru, package = "innovar")

malaria_cases_pob_sf <- Peru %>%
  filter(dep == "LORETO") %>%
  select(District = distr, geometry) %>% 
  right_join(
    malaria_cases_pob
  )
```


```{r}
figure1 <- ggplot(malaria_cases_pob_sf) +
  geom_sf(aes(fill = api, geometry = geometry)) +
  geom_sf(data = malaria_cases_pob_sf %>% dplyr::filter(District == "BELEN"), colour = "#aa6439", fill = NA, size = 1.5, aes(fill = api, geometry = geometry)) +
  geom_sf(data = malaria_cases_pob_sf %>% dplyr::filter(District == "INDIANA"), colour = "#256e5d", fill = NA, size = 1.5, aes(fill = api, geometry = geometry)) +
  scale_fill_distiller(
    name = "API",
    na.value = "black",
    # limits = c(0, 4000),
    palette = "RdYlGn",
    direction = -1,
    breaks = scales::pretty_breaks(n = 5),
    values = c(
      0,
      0.001,
      0.002,
      0.005,
      0.008,
      0.01,
      0.02,
      0.03,
      0.05,
      0.1,
      0.6,
      0.9,
      1
    )
  ) +
  labs(
    x = NULL,
    y = NULL,
    title = NULL
  ) +
  theme_classic() +
  geom_sf_label_repel(
    data = malaria_cases_pob_sf %>% dplyr::filter(District == "BELEN"),
    aes(label = District),
    min.segment.length = 0,
    force = 100,
    nudge_x = -1,
    seed = 10,
    colour = "#aa6439"
  ) +
  geom_sf_label_repel(
    data = malaria_cases_pob_sf %>% dplyr::filter(District == "INDIANA"),
    aes(label = District),
    min.segment.length = 0,
    force = 100,
    nudge_x = 1,
    seed = 10,
    colour = "#256e5d"
  )

figure1
```

```{r eval=FALSE}
ggsave(
  "./02_output/plots/figure1.png",
  figure1,
  device = grDevices::png,
  dpi = 300
)
```

# Aditional descriptives

```{r}
interpretCI::propCI_sub(ffi_total, "any_pv_pf_exposure") %>% 
  magrittr::extract2("result") %>% 
  select(p, lower, upper) %>% 
  mutate(
    across(everything(), ~ formattable::percent(., digits = 1)),
  )
```

```{r}
interpretCI::propCI_sub(ffi_total, "pf_exposure") %>% 
  magrittr::extract2("result") %>% 
  select(p, lower, upper) %>% 
  mutate(
    across(everything(), ~ formattable::percent(., digits = 1)),
  )

interpretCI::propCI_sub(ffi_total, "pv_exposure") %>% 
  magrittr::extract2("result") %>% 
  select(p, lower, upper) %>% 
  mutate(
    across(everything(), ~ formattable::percent(., digits = 1)),
  )
```

# Segmented regression

```{r}
lm()
```



